---
title: "Parameter Estimation – Wild Fish Catch"
author: "Shelby Walsh"
date: "3/7/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(boot)
library(gt)
library(patchwork)
library(broom)
library(nlstools)
library(tidyr)
library(lubridate)
library(tsibble)
library(feasts)
library(GGally)
library(broom)
library(jtools)
library(scales)
library(kableExtra)
```


```{r}
fish <- read_csv("fish_catch.csv") %>% 
  clean_names() %>% 
  rename("year" = world_wild_fish_catch_and_farmed_fish_production_1950_2012,
         "wild_catch" = x2,
         "farmed" = x3,
         "total" = x4) %>% 
  slice(-(1:4)) %>% 
  mutate("y" = c(0:66)) %>% 
  head(63) 

```

```{r}
wild <- fish %>% 
  select(wild_catch, y) 

wild <- transform(wild, wild_catch = as.numeric(wild_catch))

ggplot(data = wild, aes(x = y, y = wild_catch)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Year",
       y = "Global Wild Caught Fish in Millions of Tonnes")

```

#### The exploritoty graph above shows the Global wild fish catch from 1950-2012. When we look at the graph, the overall trend of wild catch is similar to that of logistic growth. This type of growth can be demonstrated through the following euation: 
$P(t)=\frac{K}{1+Ae^{-kt}}$

When we look at the graph, $K$ or the carrying capacity seems to fall around 90 million tonnes. If our carrying capacity is 90, then our $A$ term will be 4.2: $A=\frac{K-P_o}{P_o}$

```{r}
wild_exp <- wild %>% 
  filter(y < 40) %>% 
  mutate(ln_wild = log(wild_catch))

lm_wild <- lm(ln_wild ~ y, data = wild_exp)
lm_wild
```


```{r}
wild_nls <- nls(wild_catch ~ K/(1 + A*exp(-r*y)),
              data = wild,
              start = list(K = 90, A = 4.2, r = 0.035),
              trace = TRUE
              )

summary(wild_nls)

model_out <- broom::tidy(wild_nls) 

model_out %>% 
  kbl(caption = "**Table 1.** Parameters of Logistic Growth Model for Wild Catch Fish") %>%
  kable_classic(full_width = F, html_font = "Cambria") 

wild_est <- model_out$estimate[2]
```

Our model with estimated parameters is:
$$P(t) = \frac{100.2}{1+4.316e^{-0.069t}}$$

```{r}
wild_predict <- predict(wild_nls)

# Bind predictions to original data frame:
wild_complete <- data.frame(wild, wild_predict)

# Plot them all together:
ggplot(data = wild_complete, aes(x = y, y = wild_catch)) +
  geom_point() +
  geom_line(aes(x = y, y = wild_predict), color = "darkblue") +
  theme_minimal() +
  labs(x = "Time",
       y = "Fish in Millions of Tonnes",
       title = "Global Wild Catch Fish from 1950-2012 and Predicted Catch Growth") +
  annotate(geom = "text",
           x= 25,
           y = 69,
           label = "Predicted logistic growth",
           size = 3,
           color = "darkblue") +
  theme(plot.title = element_text(size = 14,
                                   face = "bold",
        hjust = 0.5),
        axis.title.y = element_text(size = 12),
        axis.title.x = element_text(size = 12))
```

```{r}

wild_ci <- confint2(wild_nls)
wild_ci
```

